Crystal-amorphous interface induced by graphene nano-knot

### 2017-07-02 latex/paper.tex
update run.py and adjust pictures

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-07-02 16:14:21
\documentclass[%
 reprint,
 amsmath,amssymb,
 aps,
prb,
]{revtex4-1}
\preprint{APS/123-QED}
\usepackage{graphicx}% Include figure files
\usepackage{bm}% bold math
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\begin{document}
\title{Crystal-amorphous interface induced by graphene nano-knot}
\author{Yang Zhou${}^{1,2}$}
\author{Zhi-Xin Guo${}^{3}$}
\author{Shi-you Chen}
\author{Hongjun Xiang}
\author{Xin-Gao Gong${}^{1,2}$}
\email{xggong@fudan.edu.cn}
\affiliation{%
  ${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
  ${}^2$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China\\
  ${}^3$Department of Physics, Xiangtan University, Xiangtan 411105, China
}%
\begin{abstract}
  Mechanical and thermal transport properties of graphene nanoribbon knots, are systematically investigated using nonequilibrium molecular dynamics. It is found that the thermal conductivity of the ribbon decreases largely due to the presence of the knots as a defect, but with the increasing of strain, the Kapitza resistance decreases, which is due to a tighter contacting of the ribbon with itself or the other. Local phonon analysis is applied to the contacting regime to reveal the influence of the contacts on the transport. This work would be helpful for a deeper understanding of thermal conducting at nanoscale and give a guidance to the field of phonon management material design.
  \begin{description}
    \item[Keywords]
          Thermal conductivity,graphene, knot , molecular dynamics ,amorphous
  \end{description}
\end{abstract}

@@

\begin{figure}[b]
  \includegraphics[width=\textwidth]{images/structure}
  \caption{\label{fig:structure}  (color online) The perspective view of a graphene knot}
\end{figure}

@@

Before transport study, we have to access knowledge about the strain effect on the knot. The right end of the system is moved along x direction by a very slow velocity to apply accumulate strain ( $0.01 \angstrom / ps$ ) ,just the same operation in experiment. The stress is calculated with Vitual Therom and averaged in every 1000 steps. Fig.\ref{fig:stress} shows the break test of the knot. Under strain of 7\% the system is in it's unique stable state and it's unrelated to the initial seed. The remained stress at strain=0 is needed to prevent  the knot from release. At about 2\% there's a sudden small drop origin from bond reconstruction. At 7\% the knot break. But the knot doesn't break down, but results in another structure with inreversibility. All of the samples don't break down here. After a constant increasement of the strain the stress presents increasing fluctuate which is due to the soften of the structure which make it inconverge within the average steps. Some of the samples doesn't break even until the total stress exceed the first break critical stress. Some of them break down, but some of them keep connected but present a one-atom chain state. Between every breaks the stress-strain curve presents nearly linear and certain Young's modules.
The breaking happens at the entrance of the knot.
It's reasonable to study the properties only under stain of 5\%.
Knots ensemble shows a plastic future while graphene break very certainly.
\begin{figure}[b]
  \includegraphics[width=\textwidth]{images/stress}
  \caption{\label{fig:stress}  (color online) The Stres-Strain curve from 0 to a very large strain where the structures break. a) Several simulations of different random seed for MD initialization. b) The average Stress-strain curve calculated with 200 seeds. The standard error is also shown as grey ribbon.}
\end{figure}

To have a global vision of the break process we carried out more analysis on the break data as shown in Fig.\ref{fig:drop}. From figure Fig.\ref{fig:drop}a we found that the first drop happens at around 7\%  and the distribution is pretty concentrate. While the second break happens when the strain is bwteen 10\% to 40\% and is obviously broaded. This state is unstable and could be either break right after the first break or hold for a large range of strain. The 3rd and 4th breaks happens almost at the same range and has a wider range.The Young's modules distribution of the states between all the break is shown in Fig.\ref{fig:drop}b. The value at aboutn $220GP/m$ present for the modules of unbreak knot and this value is much smaller than that of graphene ribbon of $900GP/m$. The rest of the modules exhibit a slow decrease from 0 to $300GP/m$ and most of them are below 150 $300GP/m$ ,which shows that the system is softer.Fig.\ref{fig:drop}c shows the probobility of total break times when considering strain in range 0 to 1.0. The distribution exhibit a long tail.  Most of the samples break down within two or three times while that of four to five also have relative big probability. In the extreme situation the system could break up to 9 times. Fig.\ref{fig:drop}d shows the the probability of break down. Below 0.07 there's no probability of breaking down and the structure is stable. when above 0.07 there's about 2\% samples break down. With the strain increase the system has larger probability to break down, however the probability increase slower and slower which is due to the softer feature of the filament and the same strain contributes lesser
stress so the lesser probability of break down. When the strain reaches about 0.9 all the samples must have broken down.

\begin{figure}[b]
  \includegraphics[width=\textwidth]{images/drop}
  \caption{\label{fig:drop}  (color online) break properties statistics. a) The strain distribution of the first ,second drop and so on. b) The Young's modules distribution of the system between breaks. c) The total break times distrubution. d) The distribution of strain when the system is completely breaks}
\end{figure}

@@

\begin{figure}[b]
  \includegraphics[width=\textwidth]{images/cycle}
  \caption{\label{fig:cycle}  (color online) The Stree-Strain curve of a cycle process, where strain change slowly from 0 to max and then reduce from max to min and then back to 0. After every change 1000 steps NVT simulation is used to statistic the average stress. a) The curve for knot. b) The curve for graphene nano ribbin.}
\end{figure}

Graphene exhibit excellent transport properties but the present of knot defect will largely reduce the value and it's unknown whether the stress affects the thermal transportation properties. Fig.\ref{fig:tc_lx} shows the
thermal conductivity versus strain of different length. The strain have ignorable influence on the thermal condcutivity. However the strain effect of graphene is very clear. This is because the strain is eliminated by the out-of-plane displacement which has little influence on the in-plane bond length.
\begin{figure}[b]
  \includegraphics[width=\textwidth]{images/tc_lx}
  \caption{\label{fig:tc_lx}  (color online) The perspective view of a graphene knot}
\end{figure}

@@

\begin{figure}[b]
  \includegraphics[width=\textwidth]{images/tc_nx}
  \caption{\label{fig:tc_nx}  (color online) The position is normilzed to 1.0 }
\end{figure}

@@

\begin{figure}[b]
  \includegraphics[width=\textwidth]{images/dos}
  \caption{\label{fig:dos}  (color online) The position is normilzed to 1.0 }
\end{figure}

>>>>

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-07-02 16:41:05
\documentclass[%
 reprint,
 amsmath,amssymb,
 aps,
prb,
]{revtex4-1}
\preprint{APS/123-QED}
\usepackage{graphicx}% Include figure files
\usepackage{bm}% bold math
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\begin{document}
\title{Crystal-amorphous interface induced by graphene nano-knot}
\author{Yang Zhou${}^{1,2}$}
\author{Zhi-Xin Guo${}^{3}$}
\author{Shi-you Chen}
\author{Hongjun Xiang}
\author{Xin-Gao Gong${}^{1,2}$}
\email{xggong@fudan.edu.cn}
\affiliation{%
  ${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
  ${}^2$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China\\
  ${}^3$Department of Physics, Xiangtan University, Xiangtan 411105, China
}%
\begin{abstract}
  Mechanical and thermal transport properties of graphene nanoribbon knots, are systematically investigated using nonequilibrium molecular dynamics. It is found that the thermal conductivity of the ribbon decreases largely due to the presence of the knots as a defect, but with the increasing of strain, the Kapitza resistance decreases, which is due to a tighter contacting of the ribbon with itself or the other. Local phonon analysis is applied to the contacting regime to reveal the influence of the contacts on the transport. This work would be helpful for a deeper understanding of thermal conducting at nanoscale and give a guidance to the field of phonon management material design.
  \begin{description}
    \item[Keywords]
          Thermal conductivity,graphene, knot , molecular dynamics ,amorphous
  \end{description}
\end{abstract}

@@

\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/structure}
  \caption{\label{fig:structure}  (color online) The perspective view of a graphene knot}
\end{figure}

@@

Before transport study, we have to access knowledge about the strain effect on the knot. The right end of the system is moved along x direction by a very slow velocity to apply accumulate strain ( $0.01 \angstrom / ps$ ) ,just the same operation in experiment. The stress is calculated with Vitual Therom and averaged in every 1000 steps. Fig.\ref{fig:stress} shows the break test of the knot. Under strain of 7\% the system is in it's unique stable state and it's unrelated to the initial seed. The remained stress at strain=0 is needed to prevent  the knot from release. At about 2\% there's a sudden small drop origin from bond reconstruction. At 7\% the knot break. But the knot doesn't break down, but results in another structure with inreversibility. All of the samples don't break down here. After a constant increasement of the strain the stress presents increasing fluctuate which is due to the soften of the structure which make it inconverge within the average steps. Some of the samples doesn't break even until the total stress exceed the first break critical stress. Some of them break down, but some of them keep connected but present a one-atom chain state. Between every breaks the stress-strain curve presents nearly linear and certain Young's modules.
The breaking happens at the entrance of the knot.
It's reasonable to study the properties only under stain of 5\%.
Knots ensemble shows a plastic future while graphene break very certainly.
\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/stress}
  \caption{\label{fig:stress}  (color online) The Stres-Strain curve from 0 to a very large strain where the structures break. a) Several simulations of different random seed for MD initialization. b) The average Stress-strain curve calculated with 200 seeds. The standard error is also shown as grey ribbon.}
\end{figure}

To have a global vision of the break process we carried out more analysis on the break data as shown in Fig.\ref{fig:drop}. From figure Fig.\ref{fig:drop}a we found that the first drop happens at around 7\%  and the distribution is pretty concentrate. While the second break happens when the strain is bwteen 10\% to 40\% and is obviously broaded. This state is unstable and could be either break right after the first break or hold for a large range of strain. The 3rd and 4th breaks happens almost at the same range and has a wider range.The Young's modules distribution of the states between all the break is shown in Fig.\ref{fig:drop}b. The value at aboutn $220GPa/m$ present for the modules of unbreak knot and this value is much smaller than that of graphene ribbon of $900GPa/m$. The rest of the modules exhibit a slow decrease from 0 to $300GPa/m$ and most of them are below 150 $300GPa/m$ ,which shows that the system is softer.Fig.\ref{fig:drop}c shows the probobility of total break times when considering strain in range 0 to 1.0. The distribution exhibit a long tail.  Most of the samples break down within two or three times while that of four to five also have relative big probability. In the extreme situation the system could break up to 9 times. Fig.\ref{fig:drop}d shows the the probability of break down. Below 0.07 there's no probability of breaking down and the structure is stable. when above 0.07 there's about 2\% samples break down. With the strain increase the system has larger probability to break down, however the probability increase slower and slower which is due to the softer feature of the filament and the same strain contributes lesser
stress so the lesser probability of break down. When the strain reaches about 0.9 all the samples must have broken down.

\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/drop}
  \caption{\label{fig:drop}  (color online) break properties statistics. a) The strain distribution of the first ,second drop and so on. b) The Young's modules distribution of the system between breaks. c) The total break times distrubution. d) The distribution of strain when the system is completely breaks}
\end{figure}

@@

\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/cycle}
  \caption{\label{fig:cycle}  (color online) The Stree-Strain curve of a cycle process, where strain change slowly from 0 to max and then reduce from max to min and then back to 0. After every change 1000 steps NVT simulation is used to statistic the average stress. a) The curve for knot. b) The curve for graphene nano ribbin.}
\end{figure}

Graphene exhibit excellent transport properties but the present of knot defect will largely reduce the value and it's unknown whether the stress affects the thermal transportation properties. Fig.\ref{fig:tc_lx} shows the
thermal conductivity versus strain of different length. The strain have ignorable influence on the thermal condcutivity. However the strain effect of graphene is very clear. This is because the strain is eliminated by the out-of-plane displacement which has little influence on the in-plane bond length.
\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/tc_lx}
  \caption{\label{fig:tc_lx}  (color online) The perspective view of a graphene knot}
\end{figure}

@@

\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/tc_nx}
  \caption{\label{fig:tc_nx}  (color online) The position is normilzed to 1.0 }
\end{figure}

@@

\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/dos}
  \caption{\label{fig:dos}  (color online) The position is normilzed to 1.0 }
\end{figure}
